\section*{会议摘要}
\begin{etaremune}
\item Wu S., \Yao, Wang K., Wei S., Hubbard J., Wang Y., Wang K., Liu Q., \& Tong, P. (2020)
    An integrated 3d velocity structure and earthquake source imaging in Myanmar region.
    2020 AOGS 17th Annual Meeting, Hongcheon, Gangwon, South Korea (SE05-A007). (cancelled due to COVID-19)
\item
    Wei S., Wu S., \Yao, Fadil W., Wang Y., Hubbard J., \& Tong, P. (2020)
    Subduction dynamics in Myanmar, Southeast Asia revealed by ambient noise tomography.
    2020 AOGS 17th Annual Meeting, Hongcheon, Gangwon, South Korea (SE05-A014). (cancelled due to COVID-19)
\item
    Wu S., \Yao, Wang K., Wei S., Liu Q., Hubbard J., \& Tong, P. (2019)
    3-D crustal and uppermost mantle shear wave velocity model of Myanmar, Southeast Asia from ambient noise tomography.
    2019 AGU Fall Meeting, San Francisco, CA, USA (\href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/511238}{S11C-0353}).
\item
    \Yao, Liu S., Chen M., Wei S., Hubbard J., \& Tong, P. (2019)
    Joint regional earthquake and teleseismic traveltime tomography of Myanmar.
    2019 AGU Fall Meeting, San Francisco, CA, USA (\href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/532179}{T14B-05}, Oral).
\item
    \Yao, \& Tong, P. (2018)
    First finite-frequency tomography of Myanmar.
    2018 AGU Fall Meeting, Washington, D.C., USA (\href{http://adsabs.harvard.edu/abs/2018AGUFM.S53C0418Y}{S53C-0418}).
\item
    Tian, D., \Yao, \& Wen, L. (2017)
    Collapse and earthquake swarm after North Korea's 3 September 2017 nuclear test.
    2017 AGU Fall Meeting, New Orleans, LA, USA (\href{http://adsabs.harvard.edu/abs/2017AGUFM.S43H2968T}{S43H-2968}).
\item
    \Yao, Tian, D., \& Wen, L. (2017)
    High-precision location, yield and tectonic release of North Korea's 3 September 2017 nuclear test.
    2017 AGU Fall Meeting, New Orleans, LA, USA (\href{http://adsabs.harvard.edu/abs/2017AGUFM.S43H2967Y}{S43H-2967}).
\item
    \Yao, Tian, D., Sun, L., \& Wen, L. (2017)
    Temporal change of seismic Earth's inner core phases: inner core differential rotation or temporal change of inner core surface?.
    2017 AGU Fall Meeting, New Orleans, LA, USA (\href{http://adsabs.harvard.edu/abs/2017AGUFMDI33B0405Y}{DI33B-0405}).
\item
    \Yao, Tian, D., Sun, L., \& Wen, L. (2017)
    Temporal change of seismic Earth’s inner core phases: inner core super-rotation or temporal change of inner core surface?.
    Gordon Research Conference: Interior of the Earth, South Hadley, MA, USA.
\item
    \Yao, \& Wen, L. (2015)
    Temporal change of the Earth's inner core boundary beneath North Pacific and Eurasia.
    2015 AGU Fall Meeting, San Francisco, CA, USA (\href{http://adsabs.harvard.edu/abs/2015AGUFMDI33A2608Y}{DI33A-2608}).
\item
    \Yao, \& Wen, L. (2014)
    New seismic evidence for localized temporal change of the Earth's inner core boundary.
    2014 AGU Fall Meeting, San Francisco, CA, USA (\href{http://adsabs.harvard.edu/abs/2014AGUFMDI31A4261Y}{DI31A-4261}).
\item
    \Yao, \& Wen, L. (2013)
    Seismic scattering and velocity structure near the Earth's core-mantle boundary beneath the South China Sea and north Indonesia.
    2013 AGU Fall Meeting, San Francisco, CA, USA (\href{http://adsabs.harvard.edu/abs/2013AGUFMDI23A2289Y}{DI23A-2289}).
\item
    \Yao, \& Wen, L. (2012)
    Strong seismic scatterers near the Earth's core-mantle Boundary in the location of the past Sunda subduction.
    2012 AGU Fall Meeting, San Francisco, CA, USA (\href{http://adsabs.harvard.edu/abs/2012AGUFMDI31B2395Y}{DI31B-2395}).
\end{etaremune}
