\section*{学术报告}
\begin{etaremune}
\item
    \Yao\
    Slab models beneath central Myanmar revealed by body-wave traveltime tomography.
    \textit{The Academic Forum about Tectonics and Geophysics for Young Scientists in Nanjing University}, Nanjing, China.
    Jan. 7, 2021.
\item
    \Yao\
    Slab morphology beneath central Myanmar revealed by body-wave traveltime tomography.
    \textit{The 5th International Academic Forum for Young Scientists in Tongji University}, Shanghai, China.
    May 30, 2020.
    \invited
    \link{https://mgg.tongji.edu.cn/41/30/c10075a147760/page.htm}
\item
    \Yao\
    Joint regional earthquake and teleseismic traveltime tomography of Myanmar.
    \textit{2019 AGU Fall Meeting, San Francisco}, CA, USA.
    Dec. 9, 2019.
    \link{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/532179}
\item
    \Yao\
    Seismic monitoring of North Korea’s 2017 nuclear test and its triggered seismicity.
    \textit{Institute of Geodesy and Geophysics, Chinese Academy of Sciences}, Wuhan, China.
    May 30, 2019.
    \invited
\item
    \Yao\
    Seismic monitoring of North Korea’s 2017 nuclear test and its triggered seismicity.
    \textit{Center for Gravitational Experiments, Huazhong University of Science and Technology}, Wuhan, China.
    May 30, 2019.
    \link{http://ggg.hust.edu.cn/info/1494/4765.htm}
\item
    \Yao\
    Location and source characteristics of North Korea’s 2017 nuclear test and its triggered seismicity.
    \textit{Earth Observatory of Singapore}, Singapore.
    Sep. 14, 2018.
    \invited
    \link{https://earthobservatory.sg/events/location-and-source-characteristics-north-korea\%E2\%80\%99s-2017-nuclear-test-and-its-triggered}
\item
    \Yao\
    Detection and location of small seismic events.
    \textit{a workshop of seismic algorithm and program at University of Science and Technology of China}, Hefei, China.
    Jul. 3, 2018.
    \invited
\item
    \Yao\
    Seismic monitoring of North Korea’s 3 September nuclear test.
    \textit{Institute of Geology and Geophysics, Chinese Academy of Sciences}, Beijing, China.
    Jun. 15, 2018.
    \invited
\item
    \Yao\
    Temporal change of seismic Earth’s inner core phases: inner core differential rotation or temporal change of inner core surface?.
    \textit{Institute of Geology and Geophysics, Chinese Academy of Sciences}, Beijing, China.
    Jun. 15, 2018.
    \invited
\item
    \Yao\
    Temporal change of the Earth’s inner core surface and seismic monitoring of North Korea’s 3 September nuclear test.
    \textit{Institute of Earthquake Forcasting, China Earthquake Administration}, Beijing, China.
    Jun. 14, 2018.
\item
    \Yao\
    Seismic monitoring of North Korea’s 3 September nuclear test.
    \textit{China Earthquake Networks Center}, Beijing, China.
    Jun. 12, 2018.
\item
    \Yao\
    Temporal change of seismic Earth’s inner core phases: inner core differential rotation or temporal change of inner core surface?.
    \textit{2017 Annual Meeting of Chinese Geoscience Union (CGU)}, Beijing, China.
    Oct. 17, 2017.
    \invited
\item
    \Yao\
    Temporal change of the Earth’s inner core boundary.
    \textit{China Earthquake Networks Center}, Beijing, China.
    Jun. 30, 2016.
    \invited
\end{etaremune}
